---
title: "00-Adult-Length"
author: "Laura H Spencer"
date: "4/23/2021"
output: html_document
---

# Assess adult oyster length after temperature treatment, pH treatment. 

NOTE: Population codes are as follows: 
- NF= Fidalgo Bay (FB)
- HL= Dabob Bay (DB)
- SN= Oyster Bay Cohort 1 (OB1)
- K= Oyster Bay Cohort 2 (OB2) - I remove the "K" population, we don't have expression data for those adults 


```{r}
broodstock.length <- read.csv("../raw-data/broodstock-length-data.csv", header=T, na.strings = NA) %>%
    mutate_each_(funs(factor(.)),c("Population", "Temperature", "pH")) %>% filter(Population!="K") %>% droplevels() 

# Change factor orders for plots 
broodstock.length$pH <- factor(broodstock.length$pH, levels = c("Pre-pH",  "Low", "Ambient"))
broodstock.length$Population <- factor(broodstock.length$Population, levels = c("HL", "NF", "SN", "K"))
broodstock.length$Temperature <- factor(broodstock.length$Temperature, levels = c(6, 10))
brood.col.lengths <- c("white","gray55","gray85")[as.numeric(broodstock.length$pH)]
names(brood.col.lengths) <-broodstock.length$pH
```

# Explore data via plots 
```{r}
    
ggplot(data = subset(broodstock.length, pH!="Pre-pH")) + theme_minimal() + 
    geom_boxplot(aes(x=Temperature:pH, y=Weight/Length, col=Temperature:pH)) + facet_wrap(~Population)

# Size by temp (before pH exposures)
ggplot(data = subset(broodstock.length, pH=="Pre-pH"), aes(x=Temperature, y=Length)) + 
    theme_minimal() + geom_boxplot() + 
    geom_jitter(aes(col=Population)) #+ facet_wrap(~Population, nrow = 1)

# Size by temp & pH (after pH exposures)
ggplot(data = subset(broodstock.length, pH!="Pre-pH"), aes(x=Temperature:pH, y=Length)) + 
    theme_minimal() + geom_boxplot() + 
    geom_jitter(aes(col=Population)) #+ facet_wrap(~Population, nrow = 1)

# Size by pH (after pH exposures)
ggplot(data = broodstock.length, aes(x=pH, y=Length, col=pH)) + 
    theme_minimal() + geom_boxplot() + 
    geom_jitter()

# Weight by pH (after pH exposures)
ggplot(data = broodstock.length, aes(x=pH, y=Weight, col=pH)) + 
    theme_minimal() + geom_boxplot() + 
    geom_jitter()

# Size by pH (after pH exposures) - each population 
ggplot(data = broodstock.length, aes(x=pH, y=Length, col=pH)) + 
    theme_minimal() + geom_boxplot() + 
    geom_jitter() + facet_wrap(~Population, nrow = 1)

# weight by pH (after pH exposures) - each population
ggplot(data = broodstock.length, aes(x=pH, y=Weight, col=pH)) + 
    theme_minimal() + geom_boxplot() + 
    geom_jitter() + facet_wrap(~Population, nrow = 1)

# Size by temp & pH (after pH exposures)
require(plotly)
ggplotly(ggplot(data = subset(broodstock.length, Population!="K"), aes(x=Temperature:pH, y=Length)) + 
    theme_minimal() + geom_boxplot() + theme(axis.text.x=element_text(angle=45)) +
    geom_jitter(aes(col=Population)))

ggplotly(ggplot(data = subset(broodstock.length, Population!="K" & pH!="Pre-pH"), aes(x=Temperature:fct_rev(pH), y=Length)) + 
    theme_minimal() + geom_boxplot() + theme(axis.text.x=element_text(angle=45)) +
    geom_jitter(aes(col=Population)))

ggplotly(ggplot(data = subset(broodstock.length, Population!="K"), aes(x=Temperature:pH, y=Length)) + 
    theme_minimal() + geom_boxplot() + theme(axis.text.x=element_text(angle=45)) +
    geom_jitter(aes(col=Population)) + facet_wrap(~Population, nrow = 1))
```


# Mean lengths 
```{r}
aggregate(Length ~ Population + pH + Temperature, data=broodstock.length, mean)
aggregate(Length ~ Population + pH, data=broodstock.length, mean)
aggregate(Length ~ Population, data=broodstock.length, mean)

# Mean length pre-pH treatment 
aggregate(Length ~ Population, data=subset(broodstock.length, pH!="Pre-pH"), mean)
aggregate(Length ~ Population, data=subset(broodstock.length, pH!="Pre-pH"), sd)
```

# Check length data for normality 
```{r}
qqnorm(broodstock.length$Length)
hist(broodstock.length$Length)
```

Test for sign. differences among treatments _after_ temperature treatments but _before_ pCO2 treatments  

```{r}
anova(lm(Length ~ Temperature, data=subset(broodstock.length, pH=="Pre-pH"))) #No eff. of temp  
Anova(lmer(Length ~ Temperature + (1|Population), data=subset(broodstock.length, pH=="Pre-pH")), type=2) #no
```

# Length differences after pH treatments? 

```{r}
anova(lm(Length ~ pH, data=subset(broodstock.length, pH!="Pre-pH"))) #No
```

# Length differences after pH treatments compared to before? 

```{r}
Anova(lm(Length ~ Temperature*pH, data=broodstock.length), type=2) #no interaction. Assess using type II sums of squares, where I look at effects of pH and temperature after controlling for the other factor 
Anova(lm(Length ~ pH + Temperature:pH, data=broodstock.length), type=2) #pH sign. BUT that includes a "pre-pH" treat - so need to check that out. 
TukeyHSD(aov(Length ~ pH, data=broodstock.length), type=2) 
```

Try mixed effect model, with Population as random effect

```{r}
display(lmer(Length ~ Temperature*pH + (1|Population), data=broodstock.length))
Anova(lmer(Length ~ Temperature*pH + (1|Population), data=broodstock.length), type=2)

display(lmer(Length ~ pH+ (1|Population), data=broodstock.length)) 
Anova(lmer(Length ~ pH + (1|Population), data=broodstock.length), type=2) #with Pop as random effect and using type II SS, still sign. influence of temp and pH. But remember "pH" still includes the pre=pCO2 treatment 
```

# ============= I think the most appropriate stats begin here! =================
# Compare sizes by each population 

Test for sign. differences among treatments _after_ temperature treatments but _before_ pCO2 treatments  

```{r}
summary(aov(Length ~ Population*Temperature, data=subset(broodstock.length, pH=="Pre-pH"))) #No eff. of temp, but definitely Pop=specific size 
TukeyHSD(aov(Length ~ Population, data=subset(broodstock.length, pH=="Pre-pH")))
```

# Length differences after pH treatments? 

```{r}
summary(aov(Length ~ Population*Temperature*pH, data=subset(broodstock.length, pH!="Pre-pH"))) #No diff. among temperature or pH treatments, nor interaction 
TukeyHSD(aov(Length ~ Population*Temperature*pH, data=subset(broodstock.length, pH!="Pre-pH")))

#what about weight?
summary(aov(Weight ~ Population*Temperature*pH, data=subset(broodstock.length, pH!="Pre-pH"))) #No diff. among temperature or pH treatments, nor interaction 
```

# Length differences after pH treatments compared to before? 

```{r}
summary(aov(Length ~ pH/Population, data=broodstock.length)) # all combined - population and pH effects only, but that includes pre-pH)

# Now look at population-specific changes in size between pre-pCO2 and after ambient, high pCO2 
summary(aov(Length ~ pH, data=subset(broodstock.length, Population=="HL"))) # Dabob Baby - no differences between any pco2 (pre, ambient, high)
TukeyHSD(aov(Length ~ pH, data=subset(broodstock.length, Population=="HL")))

summary(aov(Length ~ pH, data=subset(broodstock.length, Population=="NF"))) # Fidalgo Baby - yes, difference somewhere, but where? 
TukeyHSD(aov(Length ~ pH, data=subset(broodstock.length, Population=="NF"))) #FB kinda larger after ambient pCO2 compared to before 

summary(aov(Length ~ pH, data=subset(broodstock.length, Population=="SN"))) # Oyster Baby - yes, difference somewhere, but where? 
TukeyHSD(aov(Length ~ pH, data=subset(broodstock.length, Population=="SN"))) #Oyster Bay much larger after ambient pCO2 compared to before 


# Any effect to weight? nope. 
summary(aov(Weight ~ Population*Temperature*pH, data=broodstock.length)) # all combined - only population effect
summary(aov(Weight ~ pH, data=subset(broodstock.length, Population=="HL"))) # Dabob Baby - no differences between any pco2 (pre, ambient, high)
summary(aov(Weight ~ pH, data=subset(broodstock.length, Population=="NF"))) # Fidalgo Baby - no differences between any pco2 (pre, ambient, high)
summary(aov(Weight ~ pH, data=subset(broodstock.length, Population=="SN"))) # Oyster Baby - no differences between any pco2 (pre, ambient, high)
```



# =======
# Figure 

```{r}
#pdf(file="Figures/broodstock-height.pdf", width=5, height = 5)
# ggplot(broodstock.length, aes(x=Population, y= Length, fill=pH)) +  geom_boxplot() + 
#   geom_point(size=1.25, position=position_jitterdodge(jitter.width = 0.18, jitter.height = 0, dodge.width = 0.75),aes(group=pH)) + 
#     labs(title=(expression(paste("Shell height by cohort, ", pCO[2], " exposure"))), y=expression("Shell height (mm)")) + 
#   theme_bw(base_size = 12) + 
#   theme(plot.title = element_text(size = 14, hjust = 0, colour = "gray30"), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.title.x = element_blank(), legend.position="bottom") +  
#     geom_vline(xintercept = c(1.5, 2.5), colour="gray") + 
#     scale_fill_manual(values=brood.col.lengths, name=element_blank(), labels = c(expression(pre-pCO[2]), expression(High-pCO[2]), expression(Ambient-pCO[2])))+
#     scale_x_discrete(labels = c('Dabob Bay','Fidalgo Bay', "Oyster Bay C1",'Oyster Bay C2')) +
#     scale_y_continuous(limits=c(min=min(broodstock.length$Length),max=max(broodstock.length$Length)))
#dev.off()

broodstock.length$treat <- as.factor(paste(broodstock.length$Temperature, broodstock.length$pH, sep="."))
broodstock.length$treat <- factor(broodstock.length$treat, levels = c("6.Pre-pH", "10.Pre-pH","6.Low","10.Low","6.Ambient","10.Ambient"))

# FIGURE FOR PAPER 
#pdf(file="Figures/broodstock-height.pdf", width=5, height = 5)
ggplot(broodstock.length, aes(x=treat, y= Length)) +  geom_boxplot() + 
  geom_point(size=1.25, position=position_jitterdodge(jitter.width = 1.5, jitter.height = 0, dodge.width = 0.75),aes(group=treat, col=Population)) + 
    labs(title=(expression(paste("Adult shell height by temperature & ", pCO[2], " exposure"))), y=expression("Shell height (mm)")) + 
  theme_bw(base_size = 12) + 
  theme(plot.title = element_text(size = 14, hjust = 0, colour = "gray30"), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        panel.background = element_blank(), axis.title.x = element_blank(), legend.position="right", 
        axis.text.x = element_text(size = 8)) +  
    geom_vline(xintercept = c(2.5, 4.5), colour="gray") + 
    scale_color_manual(values=c("#4daf4a","#377eb8","#984ea3"), labels=c("HL"="Dabob Bay", "NF"="Fidalgo Bay", "SN"="Oyster Bay C1")) + #,"#e41a1c" 
    scale_y_continuous(limits=c(min=min(broodstock.length$Length),max=1.06*max(broodstock.length$Length))) +
    annotate("text", x = 1.5, y = 48, label = "a") +
    annotate("text", x = 3.5, y = 48, label = "ab") +
    annotate("text", x = 5.5, y = 48, label = "b") +
    scale_x_discrete(labels=c("6.Pre-pH" = "6°C\n(pre-pCO2)", "10.Pre-pH" = "10°C\n(pre-pCO2)", 
                                    "6.Low" = "6°C\nHigh pCO2", "10.Low" = "10°C\nHigh pCO2", 
                                    "6.Ambient" = "6°C\nAmbient pCO2", "10.Ambient" = "10°C\nAmbient pCO2")) +
    guides(colour = guide_legend(override.aes = list(size=4.5)))
#dev.off()


# ANOTHER OPTION: FIGURE FOR PAPER 
#pdf(file="Figures/broodstock-height.pdf", width=5, height = 5)
ggplot(broodstock.length, aes(x=pH, y= Length)) +  geom_boxplot(outlier.shape = NA) + 
  geom_point(size=1.5, alpha=0.75, position=position_jitterdodge(jitter.width = .8, jitter.height = 0, dodge.width = 0.75),aes(group=treat, col=Population)) + 
    labs(title=(expression(paste("Adult shell height by, ", pCO[2], " exposure & cohort"))), y=expression("Shell height (mm)")) + 
  theme_bw(base_size = 12) + 
  theme(plot.title = element_text(size = 14, hjust = 0, colour = "gray30"), panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), panel.background = element_blank(), axis.title.x = element_blank(), legend.position="right") +  
    scale_color_manual(values=c("#4daf4a","#377eb8","#984ea3"), labels=c("HL"="Dabob Bay", "NF"="Fidalgo Bay", "SN"="Oyster Bay C1"), name="Cohort") + #,"#e41a1c" 
    scale_y_continuous(limits=c(min=min(broodstock.length$Length),max=1.06*max(broodstock.length$Length))) +
    annotate("text", x = 1, y = 48, label = "a") +
    annotate("text", x = 2, y = 48, label = "ab") +
    annotate("text", x = 3, y = 48, label = "b") +
    scale_x_discrete(labels=c("Pre-pH" = "Pre-pCO2\nExposure", "Low" = "High pCO2", 
                                    "Ambient" = "Ambient pCO2")) +
    guides(colour = guide_legend(override.aes = list(size=4.5)))
#dev.off()

# BEST FIGURE OPTION FOR PAPER, broken up by population. HAVE TO annotate by hand in powerpoint, though. (easiest way to add letters)
ggplot(broodstock.length, aes(x=pH, y= Length)) +  geom_boxplot(outlier.shape = NA) + 
  geom_point(size=1.5, alpha=0.75, position=position_jitterdodge(jitter.width = .8, jitter.height = 0, dodge.width = 0.75),
             aes(group=treat, col=Population)) + 
    labs(title=(expression(paste("Adult shell height by, ", pCO[2], " exposure & cohort"))), y=expression("Shell height (mm)")) + 
  theme_bw(base_size = 12) + 
  theme(plot.title = element_text(size = 14, hjust = 0, colour = "gray30"), panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), panel.background = element_blank(), 
        axis.title.x = element_blank(), legend.position="right", axis.text.x = element_text(size=8)) +  
    scale_color_manual(values=c("#4daf4a","#377eb8","#984ea3"), 
                       labels=c("HL"="Dabob Bay", "NF"="Fidalgo Bay", "SN"="Oyster Bay C1"), name="Cohort") + #,"#e41a1c" 
    scale_y_continuous(limits=c(min=min(broodstock.length$Length),max=1.06*max(broodstock.length$Length))) +
        scale_x_discrete(labels=c("Pre-pH" = "Pre-pCO2\nExposure", "Low" = "High\npCO2", 
                                    "Ambient" = "Ambient\npCO2")) +
    guides(colour = guide_legend(override.aes = list(size=4.5))) +
  facet_wrap(~Population, labeller = labeller(Population=c("HL"="Dabob Bay","NF"="Fidalgo Bay","SN"="Oyster Bay")))
```
# Growth plot 

```{r}
b <- broodstock.length %>% 
  group_by(Population, pH) %>%
  summarise(mean=mean(Length), sd=sd(Length)) %>% ungroup() %>%
  mutate(time=str_replace(pH, "Low|Ambient", "Post-pH")) %>%
  mutate(pH=str_replace(pH, "Pre-pH", "Ambient")) %>% 
  rbind(., subset(., time=="Pre-pH") %>% mutate(pH=str_replace(pH, "Ambient", "Low"))) 

c <- broodstock.length %>% 
  group_by(pH) %>%
  summarise(mean=mean(Length), sd=sd(Length)) %>% ungroup() %>%
  mutate(time=str_replace(pH, "Low|Ambient", "Post-pH")) %>%
  mutate(pH=str_replace(pH, "Pre-pH", "Ambient")) %>% 
  rbind(., subset(., time=="Pre-pH") %>% mutate(pH=str_replace(pH, "Ambient", "Low"))) 


# ggdotplot(data= broodstock.length %>% mutate(time=str_replace(pH, "Low|Ambient", "Post-pH")),
#                 x="time", y= "Length", color="pH") + facet_wrap(~Population)
# stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), 
#                  geom="pointrange", color="red") + 
  #geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=0.2, position=position_dodge(0.05)) +

ggplot(data=broodstock.length %>% mutate(time=str_replace(pH, "Low|Ambient", "Post-pH")),
                        aes(x=fct_rev(time), y=Length, fill=pH)) + 
  geom_dotplot(binaxis='y', stackdir='center', alpha=0.15, binwidth=1, col=NA) + 
  facet_wrap(~Population, labeller = labeller(Population=c("HL"="Dabob Bay","NF"="Fidalgo Bay","SN"="Oyster Bay"))) +
  scale_fill_manual(values=c("gray10","red","blue"), name="Treatment",
                    labels=c("Ambient"="Control", "Low"="Acidification", "Pre-pH"="Pre-Treatment")) +
  # scale_fill_manual(values=c("#67a9cf","#ef8a62"), name="Treatment",
  #                    labels=c("Ambient"="Control", "Low"="Acidification", "Pre-pH"="Pre-Treatment")) +
  geom_line(data=b, aes(x=fct_rev(time), y=mean, color=pH, group=pH)) + 
  geom_point(data=b, aes(x=fct_rev(time), y=mean, fill=pH, group=pH), color="black", size=3.5, pch=22) + 
  scale_color_manual(values=c("#67a9cf","#ef8a62"), guide="none") +
  theme_bw(base_size = 12) + 
  theme(plot.title = element_text(size = 14, hjust = 0, colour = "gray30"), panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), panel.background = element_blank(), 
        axis.title.x = element_blank(), legend.position="right", axis.text.x = element_text(size=8)) +  
          labs(title=(expression(paste("Adult shell growth by ", pCO[2], " exposure & cohort"))), 
               y=expression("Shell height (mm)")) + ylim(c(20,47))

#show_col(c('#d1e5f0','#67a9cf','#fddbc7','#ef8a62'))


# all populations combined 
# copy 525 x 675
ggplot(data=broodstock.length %>% mutate(time=str_replace(pH, "Low|Ambient", "Post-pH")),
                        aes(x=fct_rev(time), y=Length, fill=pH)) + 
  geom_dotplot(binaxis='y', stackdir='center', alpha=0.3, binwidth=.75, col=NA) + 
  #facet_wrap(~Population, labeller = labeller(Population=c("HL"="Dabob Bay","NF"="Fidalgo Bay","SN"="Oyster Bay"))) +
  scale_fill_manual(values=c("gray75","#ef8a62","#67a9cf"), name="Treatment",
                     labels=c("Ambient"="Control", "Low"="Acidification", "Pre-pH"="Pre-Treatment")) +
  #scale_fill_manual(values=c("blue","red"), name="Treatment",
  #                  labels=c("Ambient"="Control", "Low"="Acidification", "Pre-pH"="Pre-Treatment")) +
  geom_line(data=c, aes(x=fct_rev(time), y=mean, color=pH, group=pH)) + 
  geom_point(data=c, aes(x=fct_rev(time), y=mean, fill=pH, group=pH), color="black", size=4, pch=22) + 
  scale_color_manual(values=c("#67a9cf","#ef8a62"), guide="none") +
  theme_bw(base_size = 12) + 
  theme(plot.title = element_text(size = 14, hjust = 0, colour = "gray30"), panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), panel.background = element_blank(), 
        axis.title.x = element_blank(), legend.position="right", axis.text.x = element_text(size=8)) +  
          labs(title=(expression(paste("Adult shell growth by ", pCO[2], " exposure & cohort"))), 
               y=expression("Shell height (mm)")) + ylim(c(20,47))
```

# Calculate delta, then compare 

```{r}
test <- broodstock.length %>% 
  mutate(time=str_replace(pH, "Low|Ambient", "Post-pH")) %>%
  mutate(pH=str_replace(pH, "Pre-pH", "Ambient")) %>% 
  rbind(., subset(., time=="Pre-pH") %>% mutate(pH=str_replace(pH, "Ambient", "Low"))) %>%
  select(Sample, Population, pH, Length, time) %>%
  left_join(b %>% filter(time=="Pre-pH") %>% select(Population, pH, mean), by = c("Population", "pH")) %>%
  mutate(length.delta=Length-mean) %>% filter(time=="Post-pH") #%>%
#  ggplot() + geom_violin(aes(x=Population, y=length.delta, fill=pH))

hist(test$length.delta)
summary(aov(length.delta ~ pH, data=subset(test, Population=="HL")))
summary(aov(length.delta ~ pH, data=subset(test, Population=="NF")))
summary(aov(length.delta ~ pH, data=subset(test, Population=="SN")))
```


# Weight change plot 

```{r}
d <- broodstock.length %>% 
  group_by(Population, pH) %>%
  summarise(mean=mean(Weight), sd=sd(Weight)) %>% ungroup() %>%
  mutate(time=str_replace(pH, "Low|Ambient", "Post-pH")) %>%
  mutate(pH=str_replace(pH, "Pre-pH", "Ambient")) %>% 
  rbind(., subset(., time=="Pre-pH") %>% mutate(pH=str_replace(pH, "Ambient", "Low"))) 

e <- broodstock.length %>% 
  group_by(pH) %>%
  summarise(mean=mean(Weight), sd=sd(Weight)) %>% ungroup() %>%
  mutate(time=str_replace(pH, "Low|Ambient", "Post-pH")) %>%
  mutate(pH=str_replace(pH, "Pre-pH", "Ambient")) %>% 
  rbind(., subset(., time=="Pre-pH") %>% mutate(pH=str_replace(pH, "Ambient", "Low"))) 


# ggdotplot(data= broodstock.length %>% mutate(time=str_replace(pH, "Low|Ambient", "Post-pH")),
#                 x="time", y= "Weight", color="pH") + facet_wrap(~Population)
# stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), 
#                  geom="pointrange", color="red") + 
  #geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=0.2, position=position_dodge(0.05)) +

ggplot(data=broodstock.length %>% mutate(time=str_replace(pH, "Low|Ambient", "Post-pH")),
                        aes(x=fct_rev(time), y=Weight, fill=pH)) + 
  geom_dotplot(binaxis='y', stackdir='center', alpha=0.3, col=NA) + 
  facet_wrap(~Population, labeller = labeller(Population=c("HL"="Dabob Bay","NF"="Fidalgo Bay","SN"="Oyster Bay"))) +
  scale_fill_manual(values=c("gray75","#ef8a62","#67a9cf"), name="Treatment",
                    labels=c("Ambient"="Control", "Low"="Acidification", "Pre-pH"="Pre-Treatment")) +
  # scale_fill_manual(values=c("#67a9cf","#ef8a62"), name="Treatment",
  #                    labels=c("Ambient"="Control", "Low"="Acidification", "Pre-pH"="Pre-Treatment")) +
  geom_line(data=d, aes(x=fct_rev(time), y=mean, color=pH, group=pH)) + 
  geom_point(data=d, aes(x=fct_rev(time), y=mean, fill=pH, group=pH), color="black", size=3.5, pch=22) + 
  scale_color_manual(values=c("#67a9cf","#ef8a62"), guide="none") +
  theme_bw(base_size = 12) + 
  theme(plot.title = element_text(size = 14, hjust = 0, colour = "gray30"), panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), panel.background = element_blank(), 
        axis.title.x = element_blank(), legend.position="right", axis.text.x = element_text(size=8)) +  
          labs(title=(expression(paste("Adult tissue growth by ", pCO[2], " exposure & cohort"))), 
               y=expression("Tissue wet weight (g)")) 

#show_col(c('#d1e5f0','#67a9cf','#fddbc7','#ef8a62'))


# all populations combined 
# copy 525 x 675
ggplot(data=broodstock.length %>% mutate(time=str_replace(pH, "Low|Ambient", "Post-pH")),
                        aes(x=fct_rev(time), y=Weight, fill=pH)) + 
  geom_dotplot(binaxis='y', stackdir='center', alpha=0.3, binwidth=0.35, col=NA) + 
  #facet_wrap(~Population, labeller = labeller(Population=c("HL"="Dabob Bay","NF"="Fidalgo Bay","SN"="Oyster Bay"))) +
  scale_fill_manual(values=c("gray75","#ef8a62","#67a9cf"), name="Treatment",
                     labels=c("Ambient"="Control", "Low"="Acidification", "Pre-pH"="Pre-Treatment")) +
  #scale_fill_manual(values=c("blue","red"), name="Treatment",
  #                  labels=c("Ambient"="Control", "Low"="Acidification", "Pre-pH"="Pre-Treatment")) +
  geom_line(data=e, aes(x=fct_rev(time), y=mean, color=pH, group=pH)) + 
  geom_point(data=e, aes(x=fct_rev(time), y=mean, fill=pH, group=pH), color="black", size=4, pch=22) + 
  scale_color_manual(values=c("#67a9cf","#ef8a62"), guide="none") +
  theme_bw(base_size = 12) + 
  theme(plot.title = element_text(size = 14, hjust = 0, colour = "gray30"), panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), panel.background = element_blank(), 
        axis.title.x = element_blank(), legend.position="right", axis.text.x = element_text(size=8)) +  
          labs(title=(expression(paste("Adult shell growth by ", pCO[2], " exposure & cohort"))), 
               y=expression("Shell height (mm)"))
```